%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Research Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}


%------------------------------------------------    

\cventry
{PhD student. Advisor: Prof. Tiziana Di Matteo} % Job title
{The McWilliams Center for Cosmology} % Organization
{Pittsburgh, U.S.A} % Location
{Aug. 2016 - Present} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item \textbf{Project: Test the influence of different supermassive black hole seeding masses in simulation (in progress)}
\item {Ran simulations using MP-Gadget (a N-body+hydro solver) to test different seeding masses}
\item \textbf{Project: BlueTides simulation: establishing black hole-galaxy relations at high-redshift [2]}
\item {Studied the scaling relations between mass of supermassive black hole and galaxy properties in BlueTides simulation}
\end{cvitems}
}

%------------------------------------------------

\cventry
{MS student. Advisor: Prof. Tzihong Chiueh} % Job title
{Dept. of Physics, National Taiwan University} % Organization
{Taipei, Taiwan} % Location
{Jul. 2012 - Jun. 2013} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item \textbf{Thesis: Numerically solving Schrödinger equation in hydrodynamic form in expanding universe}
\item {Numerically solved the flux-conservative initial value problems of quantum wave dark matter (ψDM)}
\item \textbf{Project: Contrasting galaxy formation from ψDM with ΛCDM, using Planck and Hubble data [1]}
\item {Studied the power spectrum, transfer function, halo mass function, and luminosity function of ψDM and CDM}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Undergraduate Researcher. Advisor: Prof. Jiun-Huei Proty Wu} % Job title
{Dept. of Physics, National Taiwan University} % Organization
{Taipei, Taiwan} % Location
{Sept. 2011 - Aug. 2013} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Numerically tested the evolution of gravitational waves with different initial conditions in loop quantum cosmology}
\end{cvitems} 
}

%------------------------------------------------

\cventry
{Undergraduate Researcher. Advisor: Prof. Yih-Yuh Chen} % Job title
{Dept. of Physics, National Taiwan University} % Organization
{Taipei, Taiwan} % Location
{Sept. 2012 - Feb. 2013} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Researched Percell’s three-link swimmer and self-propelled micro-swimmers at low Reynolds number}
\end{cvitems} 
}

%------------------------------------------------

\end{cventries}